Equivalency of Proximal Compact and Corson Compact in Uniform Spaces

### 2013-12-19 articles/proximity-corson/proximity-corson.tex
noted Bells' usage of strong proximal game

\begin{abstract}
A common generalization of metric spaces is the idea of a uniform space, determined by a uniformity of entourages on the diagonal of the square. Proximal uniform spaces are those for which the first player has a winning strategy in this $\omega$-length game due to Bell: the first player chooses an entourage of the space, and her opponent chooses a point close to the point chosen in the previous round, with respect to the entourage chosen in the previous round. As proximal spaces are preserved under $\Sigma$-products, Nyikos has observed that every Corson compact space, a compact space embeddable in the $\Sigma$-product of real lines, must then be proximal. He asked if that implication may also be reversed. We answer his question postively, by way of defining a stronger version of the proximal game which is perfect-information equivalent to Bell's original game for uniformly locally compact spaces.
\end{abstract}

@@

While there is not much trouble in ensuring the nonempty intersection of\\ $\bigcap_{n<\omega} D_n[p_n]$ for this particular proof, we turned to a stronger version of $\proxgame{X}$ which avoids the issue entirely.

>>>>

\begin{abstract}
A common generalization of metric spaces is the idea of a uniform space, determined by a uniformity of entourages on the diagonal of the square. Proximal uniform spaces are those for which the first player has a winning strategy in this $\omega$-length game due to Bell: the first player chooses an entourage of the space, and her opponent chooses a point close to the point chosen in the previous round, with respect to the entourage chosen in the previous round. As proximal spaces are preserved under $\Sigma$-products, Nyikos has observed that every Corson compact space, a compact space embeddable in the $\Sigma$-product of real lines, must then be proximal. He asked if that implication may also be reversed. We answer his question postively, by way of a stronger version of the proximal game which is perfect-information equivalent to Bell's original game for uniformly locally compact spaces.
\end{abstract}

@@

While there is not much trouble in ensuring the nonempty intersection of\\ $\bigcap_{n<\omega} D_n[p_n]$ for this particular proof, we turned to a stronger version of $\proxgame{X}$ discussed briefly by Bell which avoids the issue entirely.
